\plaintitle

### 2016-12-08 drafts/labor/complexity.tex
verrrrry rough draft of moving the lit review stuff around (more info below) moving the contextual stuff from , , and  to , with the ultimate goal of putting most of the general-purpose historical background in the lit review section as a roadmap/overview of the three main threads that we use to evaluate these questions.

\topic{\citeauthor{grier2013computers} gives early accounts of
a piecework strategy in Airy's creation of
the British Nautical Almanac~\cite{grier2013computers}.}
Airy's goal was complex
--- mathematical calculations to produce tables that would
allow sailors to locate themselves by starlight from sea.
Many of his contributors did not have high--level mathematical training,
so Airy broke down the task into simpler calculations and
distributed them by mail,
accomplishing the complex goal through piecework tasks that paid little.

However, when piecework entered the American economy,
it was not used for complex work.
One reason for low complexity was workers' skills: it was infeasible to provide new pieceworkers with the comprehensive education
that apprenticeships imparted \cite{hart2013rise}.
So, initially piecework arose for farm work, and as
\citeauthor{hughRaynbirdTaskWork} and others discuss,
the practice remained relatively obscure until
it blossomed in the textile industry~\cite{hughRaynbirdTaskWork}.
Complexity levels remained low at the turn of
the \nth{20} century as piecework saturated New York City~\cite{riisOtherSideLives}.
However, writers of the time focused their attention on
wage \cite{burton1899commercial} and
management regimes \cite{norton1900textile}
rather than training.

>>>>

% \topic{\citeauthor{grier2013computers} gives early accounts of
% a piecework strategy in Airy's creation of
% the British Nautical Almanac~\cite{grier2013computers}.}
% Airy's goal was complex
% --- mathematical calculations to produce tables that would
% allow sailors to locate themselves by starlight from sea.
% Many of his contributors did not have high--level mathematical training,
% so Airy broke down the task into simpler calculations and
% distributed them by mail,
% accomplishing the complex goal through piecework tasks that paid little.

% However, when piecework entered the American economy,
% it was not used for complex work.
% One reason for low complexity was workers' skills: it was infeasible to provide new pieceworkers with the comprehensive education
% that apprenticeships imparted \cite{hart2013rise}.
% So, initially piecework arose for farm work, and as
% \citeauthor{hughRaynbirdTaskWork} and others discuss,
% the practice remained relatively obscure until
% it blossomed in the textile industry~\cite{hughRaynbirdTaskWork}.
% Complexity levels remained low at the turn of
% the \nth{20} century as piecework saturated New York City~\cite{riisOtherSideLives}.
% However, writers of the time focused their attention on
% wage \cite{burton1899commercial} and
% management regimes \cite{norton1900textile}
% rather than training.

### 2016-12-08 drafts/labor/decomposition.tex
verrrrry rough draft of moving the lit review stuff around (more info below) moving the contextual stuff from , , and  to , with the ultimate goal of putting most of the general-purpose historical background in the lit review section as a roadmap/overview of the three main threads that we use to evaluate these questions.

\topic{Piecework became an important factor in the war effort for the Second World War,
cementing its role not only in American factories,
but in industrial work around the world.}
The 1930s represented a boom for piecework on an unprecedented scale,
especially among engineering and metalworking industries.
As discussed earlier, \citeauthor{hart2013rise} characterize the 1930s
--- and more broadly the first half of the \nth{20} century ---
as the ``heyday'' of the use of piecework.
He attributes this to the shortage of male workers,
who would have gone through a conventional apprenticeship process
affording them more comprehensive knowledge of the total scope of work.
One might reflect on the observation that ``Rosie the Riveter'',
an icon of \nth{20} century America who
represented empowerment and opportunity for women \cite{honey1985creating},
was a pieceworker~\cite{davies2014origins}.

\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics,
including
`Arithmetic,
the use of Logarithms,
and Elementary Algebra'~''
to compute astronomical phenomena~\cite{grier2013computers}.
The work that Airy solicited resonates with modern crowd work for several reasons.
First,
work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
Second,
tasks were discrete
--- that is,
independent from one another.
Finally,
workers could be trained on a very narrow subset of mathematical skills to be
sufficiently qualified to do this work.

This approach found its audience in the early \nth{20} century with the rise of Fordism and scientific management (or Taylorism).
Scientific management suggested that it was possible to measure work  at unprecedented resolution and precision.
As \citeauthor{Brown01041990} points out,
piecework most greatly benefits the instrumented measurement of workers,
but certainly in Ford and Taylor's time,
highly instrumented,
automatic measurement of workers was all but impossible~\cite{Brown01041990}.
As a result,
the distillation of work into smaller units ultimately bottomed out with tasks as small as could be usefully measured~\cite{10.2307/23702539}.

\topic{Piecework researchers enumerate a number of problems with the decomposition of work,
and the conflicting pressures managers and workers put forth.}
\citeauthor{bewley1999wages} in particular points out that
the approach of paying workers by the piece is
``\dots~not practical for workers doing many tasks,
because of
the cost of establishing the rates and because
piecework does not compensate workers for time spent switching tasks''.
Ultimately, \citeauthor{bewley1999wages} argues that
``[piecework is] infeasible,
because \dots
total output is the joint product of varying groups of people''~\cite{bewley1999wages}.

>>>>

% \topic{Piecework became an important factor in the war effort for the Second World War,
% cementing its role not only in American factories,
% but in industrial work around the world.}
% The 1930s represented a boom for piecework on an unprecedented scale,
% especially among engineering and metalworking industries.
% As discussed earlier, \citeauthor{hart2013rise} characterize the 1930s
% --- and more broadly the first half of the \nth{20} century ---
% as the ``heyday'' of the use of piecework.
% He attributes this to the shortage of male workers,
% who would have gone through a conventional apprenticeship process
% affording them more comprehensive knowledge of the total scope of work.
% One might reflect on the observation that ``Rosie the Riveter'',
% an icon of \nth{20} century America who
% represented empowerment and opportunity for women \cite{honey1985creating},
% was a pieceworker~\cite{davies2014origins}.

% \topic{The research community relating to
% piecework and labor
% has been wrestling with the decomposition of work for centuries.}
% The beginnings of
% systematic task decomposition
% stretch back as far as the \nth{19} century,
% when Airy employed young boys at the Greenwich Observatory who
% ``possessed the basic skills of mathematics,
% including
% `Arithmetic,
% the use of Logarithms,
% and Elementary Algebra'~''
% to compute astronomical phenomena~\cite{grier2013computers}.
% The work that Airy solicited resonates with modern crowd work for several reasons.
% First,
% work output was quickly verifiable;
% Airy could assign variably skilled workers to compute values,
% and have other workers check their work.
% Second,
% tasks were discrete
% --- that is,
% independent from one another.
% Finally,
% workers could be trained on a very narrow subset of mathematical skills to be
% sufficiently qualified to do this work.

% This approach found its audience in the early \nth{20} century with the rise of Fordism and scientific management (or Taylorism).
% Scientific management suggested that it was possible to measure work  at unprecedented resolution and precision.
% As \citeauthor{Brown01041990} points out,
% piecework most greatly benefits the instrumented measurement of workers,
% but certainly in Ford and Taylor's time,
% highly instrumented,
% automatic measurement of workers was all but impossible~\cite{Brown01041990}.
% As a result,
% the distillation of work into smaller units ultimately bottomed out with tasks as small as could be usefully measured~\cite{10.2307/23702539}.

% \topic{Piecework researchers enumerate a number of problems with the decomposition of work,
% and the conflicting pressures managers and workers put forth.}
% \citeauthor{bewley1999wages} in particular points out that
% the approach of paying workers by the piece is
% ``\dots~not practical for workers doing many tasks,
% because of
% the cost of establishing the rates and because
% piecework does not compensate workers for time spent switching tasks''.
% Ultimately, \citeauthor{bewley1999wages} argues that
% ``[piecework is] infeasible,
% because \dots
% total output is the joint product of varying groups of people''~\cite{bewley1999wages}.

### 2016-12-08 drafts/labor/piecework_lit.tex
verrrrry rough draft of moving the lit review stuff around (more info below) moving the contextual stuff from , , and  to , with the ultimate goal of putting most of the general-purpose historical background in the lit review section as a roadmap/overview of the three main threads that we use to evaluate these questions.

\subsection{A Piecework Primer}\label{sec:pieceworkPrimer} % yay rhyming?
\topic{In this section we will offer a brief overview of the history of piecework;
this should not be mistaken for a comprehensive background.}
Instead, this section will attempt to provide a sense of orientation when thinking about piecework.
In other words, it will frame piecework in the contexts of
the early days of the Industrial Revolution,
through the political and economic turmoil of the early and mid--\nth{20} century,
and into the \nth{21} century.
While the previous section provided a \textit{definition} of piecework,
this section attempts to shine a light on the \textit{zeitgeist} of piecework.

@@

>>>>

\subsection{A Piecework Primer}\label{sec:pieceworkPrimer} % ali adores alliteration
\topic{In this section we will offer a brief overview of the history of piecework;
this should not be mistaken for a comprehensive background.}
Instead, this section will attempt to provide a sense of orientation when thinking about piecework.
In other words, it will frame piecework in the contexts of
the early days of the Industrial Revolution,
through the political and economic turmoil of the early and mid--\nth{20} century,
and into the \nth{21} century.
While the previous section provided a \textit{definition} of piecework,
this section attempts to shine a light on the \textit{zeitgeist} of piecework.

@@

\subsection{Case studies in piecework}
\topic{We'll try to discuss the context and general details of three instructive cases of piecework,
       which will substantively inform the three questions we investigate later
       (\namerefl{sec:complexity}, \namerefl{sec:decomposition}, and \namerefl{sec:relationships}).}
The three major threads we'll explore will be
\begin{inlinelist}
  \item Airy's employment of \textit{human computers},
  \item the ``matchstick'' girls, and
  \item railroad workers across the United States.
\end{inlinelist}

\subsubsection{Airy's Computers}
\topic{\citeauthor{grier2013computers} gives early accounts of
a piecework strategy in Airy's creation of
the British Nautical Almanac~\cite{grier2013computers}.}
Airy's goal was complex
--- mathematical calculations to produce tables that would
allow sailors to locate themselves by starlight from sea.
Many of his contributors did not have high--level mathematical training,
so Airy broke down the task into simpler calculations and
distributed them by mail,
accomplishing the complex goal through piecework tasks that paid little.

However, when piecework entered the American economy,
it was not used for complex work.
One reason for low complexity was workers' skills: it was infeasible to provide new pieceworkers with the comprehensive education
that apprenticeships imparted \cite{hart2013rise}.
So, initially piecework arose for farm work, and as
\citeauthor{hughRaynbirdTaskWork} and others discuss,
the practice remained relatively obscure until
it blossomed in the textile industry~\cite{hughRaynbirdTaskWork}.
Complexity levels remained low at the turn of
the \nth{20} century as piecework saturated New York City~\cite{riisOtherSideLives}.
However, writers of the time focused their attention on
wage \cite{burton1899commercial} and
management regimes \cite{norton1900textile}
rather than training.

\topic{Piecework became an important factor in the war effort for the Second World War,
cementing its role not only in American factories,
but in industrial work around the world.}
The 1930s represented a boom for piecework on an unprecedented scale,
especially among engineering and metalworking industries.
As discussed earlier, \citeauthor{hart2013rise} characterize the 1930s
--- and more broadly the first half of the \nth{20} century ---
as the ``heyday'' of the use of piecework.
He attributes this to the shortage of male workers,
who would have gone through a conventional apprenticeship process
affording them more comprehensive knowledge of the total scope of work.
One might reflect on the observation that ``Rosie the Riveter'',
an icon of \nth{20} century America who
represented empowerment and opportunity for women \cite{honey1985creating},
was a pieceworker~\cite{davies2014origins}.

\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for centuries.}
The beginnings of
systematic task decomposition
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics,
including
`Arithmetic,
the use of Logarithms,
and Elementary Algebra'~''
to compute astronomical phenomena~\cite{grier2013computers}.
The work that Airy solicited resonates with modern crowd work for several reasons.
First,
work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
Second,
tasks were discrete
--- that is,
independent from one another.
Finally,
workers could be trained on a very narrow subset of mathematical skills to be
sufficiently qualified to do this work.

This approach found its audience in the early \nth{20} century with the rise of Fordism and scientific management (or Taylorism).
Scientific management suggested that it was possible to measure work  at unprecedented resolution and precision.
As \citeauthor{Brown01041990} points out,
piecework most greatly benefits the instrumented measurement of workers,
but certainly in Ford and Taylor's time,
highly instrumented,
automatic measurement of workers was all but impossible~\cite{Brown01041990}.
As a result,
the distillation of work into smaller units ultimately bottomed out with tasks as small as could be usefully measured~\cite{10.2307/23702539}.

\topic{Piecework researchers enumerate a number of problems with the decomposition of work,
and the conflicting pressures managers and workers put forth.}
\citeauthor{bewley1999wages} in particular points out that
the approach of paying workers by the piece is
``\dots~not practical for workers doing many tasks,
because of
the cost of establishing the rates and because
piecework does not compensate workers for time spent switching tasks''.
Ultimately, \citeauthor{bewley1999wages} argues that
``[piecework is] infeasible,
because \dots
total output is the joint product of varying groups of people''~\cite{bewley1999wages}.

Workers' relationships with employers quickly soured.
The match--girls strike of 1888 was one of the earliest and most famous successful worker strikes and perhaps the beginning of ``militant trade unionism''~\cite{10.2307/3827491}.
As \citeauthor{weyer1894history} described, ``the match--girls' victory turned a new leaf in Trade Union annals''~\cite{weyer1894history}: in the 30 years after the match--girls strike, the Trade Union Movement enrollment grew from 20\% of eligible workers to over 60\%.
This strike was followed by others, including women in the garment industry in Philadelphia who established collective bargaining rights~\cite{10.2307/41829256} and national coal miners who effected an individual minimum wage in 1912~\cite{10.2307/2221944}.
The adoption of piecework's time--studies and other Taylorist and scientific management approaches reliably precipitated strikes and more generally gave workers a clear enemy against which to rally~\cite{jacoby1983union}.

\subsubsection{Human Computers}

\subsubsection{The Matchstick Girls}
\begin{itemize}
  \item foo
  \item foo
  \item foo
  \item foo
\end{itemize}

\subsubsection{Railroad Workers}
\begin{itemize}
  \item foo
  \item foo
  \item foo
  \item foo
\end{itemize}

### 2016-12-08 drafts/labor/relationships.tex
verrrrry rough draft of moving the lit review stuff around (more info below) moving the contextual stuff from , , and  to , with the ultimate goal of putting most of the general-purpose historical background in the lit review section as a roadmap/overview of the three main threads that we use to evaluate these questions.

Workers' relationships with employers quickly soured.
The match--girls strike of 1888 was one of the earliest and most famous successful worker strikes and perhaps the beginning of ``militant trade unionism''~\cite{10.2307/3827491}.
As \citeauthor{weyer1894history} described, ``the match--girls' victory turned a new leaf in Trade Union annals''~\cite{weyer1894history}: in the 30 years after the match--girls strike, the Trade Union Movement enrollment grew from 20\% of eligible workers to over 60\%.
% in the 30 years since the match--girls strike,
% the Trade Union Movement grew from
% ``20 per cent of adult male manual--working wage--earners [to] over 60 per cent''
% \cite{webb1920history}.
This strike was followed by others, including women in the garment industry in Philadelphia who established collective bargaining rights~\cite{10.2307/41829256} and national coal miners who effected an individual minimum wage in 1912~\cite{10.2307/2221944}.
The adoption of piecework's time--studies and other Taylorist and scientific management approaches reliably precipitated strikes and more generally gave workers a clear enemy against which to rally~\cite{jacoby1983union}.

@@

% \topic{While many workers participated in piecework, worker sentiment toward the practice was --- by all accounts --- mostly negative.}
% The match girls strikes which \citeauthor{10.2307/3827491} describes were just one early
% --- albeit critical ---
% case study in this space;
% the national coal strike of 1912 led to an overwhelming vote among federated coal miner pieceworkers
% to strike for
% an individual minimum wage, among other demands
% \cite{10.2307/2221944}.
% \citeauthor{10.2307/41829256} documents a series of efforts among women in the garment industries in Philadelphia to negotiate collective bargaining rights and recognition of their own labor union
% \cite{10.2307/41829256}.
% The adoption of piecework's time--studies and other Taylorist and scientific management approaches reliably precipitated strikes and more generally gave workers a clear enemy against which to rally
% \cite{jacoby1983union}.

Pieceworkers' relationships with their employers eventually developed a pattern of using 
% \topic{The questions surrounding
% the ways pieceworkers related to managers might be best answered by
% the work that has been done in the emergence and proliferation of labor unions.}
% The primary avenue for workers to interact with managers has been through
laborer advocacy groups~\cite{levi2009union,ahlquist2013interest,
      mccallum2013global,jacoby1983union}.
% (one of the forerunners of the largest and
% most politically influential labor union in the United States).
% Looking through that lens, we find copious research on
% the relationships between workers and requesters
% \cite{levi2009union,ahlquist2013interest,
%       mccallum2013global,jacoby1983union}.
Collective action grew to become a central component of negotiating with managers~\cite{russell1982collective,olsonlogic}.

\topic{Less is known about how pieceworkers related to each other.}
For one thing, the research methods we typically associate with the exploratory study of cultures
--- Anthropology, and namely participant--observation, ethnography, etc\dots ---
didn't exist quite as we know them at the turn of the \nth{20} century, and wouldn't for several more decades.
% Still, we can look at primary sources, like \citetitle{american1921problem}
% to give us some hint of how they related to each other
% \cite{american1921problem}.
Primary sources indicate that labor organizations wished for workers to identify as a collective group, 
% The driving force of American labor advocacy organizations was to get piecework railroad workers
% to identify
``not only as railroad employees but also as members of the larger life of the community''~\cite{american1921problem}.
Doing this, 
\citeauthor{ostrom1990governing} and others argued,
would facilitate collective action and perhaps collective governance~\cite{ostrom1990governing,russell1982collective,olsonlogic}.
\citeauthor{riisOtherSideLives} also contributed to this sense of shared struggle and endurance
% by the time \citetitle{american1921problem} was published
by documenting pieceworkers in their home--workplaces,
literally bringing to light the grim circumstances in which pieceworkers lived and worked~\cite{riisOtherSideLives}.

% This can also foreshadow crowd sourcing efforts like
% \TO~and \DO.

>>>>

% Workers' relationships with employers quickly soured.
% The match--girls strike of 1888 was one of the earliest and most famous successful worker strikes and perhaps the beginning of ``militant trade unionism''~\cite{10.2307/3827491}.
% As \citeauthor{weyer1894history} described, ``the match--girls' victory turned a new leaf in Trade Union annals''~\cite{weyer1894history}: in the 30 years after the match--girls strike, the Trade Union Movement enrollment grew from 20\% of eligible workers to over 60\%.
% This strike was followed by others, including women in the garment industry in Philadelphia who established collective bargaining rights~\cite{10.2307/41829256} and national coal miners who effected an individual minimum wage in 1912~\cite{10.2307/2221944}.
% The adoption of piecework's time--studies and other Taylorist and scientific management approaches reliably precipitated strikes and more generally gave workers a clear enemy against which to rally~\cite{jacoby1983union}.

@@

Pieceworkers' relationships with their employers eventually developed a pattern of using 
laborer advocacy groups~\cite{levi2009union,ahlquist2013interest,
      mccallum2013global,jacoby1983union}.
Collective action grew to become a central component of negotiating with managers~\cite{russell1982collective,olsonlogic}.

\topic{Less is known about how pieceworkers related to each other.}
For one thing, the research methods we typically associate with the exploratory study of cultures
--- Anthropology, and namely participant--observation, ethnography, etc\dots ---
didn't exist quite as we know them at the turn of the \nth{20} century, and wouldn't for several more decades.
Primary sources indicate that labor organizations wished for workers to identify as a collective group, 
``not only as railroad employees but also as members of the larger life of the community''~\cite{american1921problem}.
Doing this, 
\citeauthor{ostrom1990governing} and others argued,
would facilitate collective action and perhaps collective governance~\cite{ostrom1990governing,russell1982collective,olsonlogic}.
\citeauthor{riisOtherSideLives} also contributed to this sense of shared struggle and endurance
by documenting pieceworkers in their home--workplaces,
literally bringing to light the grim circumstances in which pieceworkers lived and worked~\cite{riisOtherSideLives}.

### 2016-12-08 drafts/labor/trackingWork.tex
intro revisions
verrrrry rough draft of moving the lit review stuff around (more info below) moving the contextual stuff from , , and  to , with the ultimate goal of putting most of the general-purpose historical background in the lit review section as a roadmap/overview of the three main threads that we use to evaluate these questions.

\usepackage{xr-hyper}
% \zxrsetup{%
%   tozreflabel=false, % not needed, since `zref` is not used otherwise
%   toltxlabel=true, % classical LaTeX labels that can be referenced with \ref, \pageref
% }
% \zexternaldocument{cases.tex}% star form: only LaTeX labels are imported

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles,appendix,endnotes}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth,endnotes,cleveref,textcase}
\usepackage[normalem]{ulem}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{mfirstuc,lastpage}
\usepackage[en-GB]{datetime2}
\usepackage{fancyhdr}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={\plaintitle},
% Use \plainauthor for final version.
%  pdfauthor={\plainauthor},
  pdfauthor={\emptyauthor},
  pdfkeywords={\plainkeywords},
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=linkColor,
  breaklinks=true,
  hypertexnames=false
}

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}
\bibliography{references}
% \addbibresource{references}

@@

% \DTMsetdatestyle{mmddyyyy}
% \DTMsetup{datesep=/}
% \pagestyle{fancy}
% \lfoot{Last compiled \today~at \DTMcurrenttime}
% \cfoot{}
% \rfoot{page \thepage/\pageref*{LastPage}}
% \fancyhead{}
% \pagenumbering{arabic}
\renewcommand{\headrulewidth}{0pt}

% \onlyinsubfile{
%   \usepackage{xr-hyper}
%   \usepackage{hyperref}
% }

\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\footnotesize}{\normalsize} % i don't need small text! (no but really remove this before submitting)
\begin{document}
\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\joke}[1]{} % don't do anything with \jokes! Just throw them away! (Better to drop it than accidentally include it)
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}

@@

\numberofauthors{3}
\author{%
  \alignauthor{Ali Alkhatib\\
    \affaddr{Stanford University}\\
    \affaddr{Stanford, USA}\\
    \email{ali.alkhatib@cs.stanford.edu}}\\
  \alignauthor{Michael Scott Bernstein\\
    \affaddr{Stanford University}\\
    \affaddr{Stanford, USA}\\
    \email{msb@cs.stanford.edu}}\\
  \alignauthor{Margaret Levi\\
    \affaddr{CASBS}\\
    \affaddr{Stanford, USA}\\
    \email{mlevi@stanford.edu}}\\
}
\author{
\alignauthor{Anonymous for submission\\
\affaddr{Affiliation fields filled}\\
    \affaddr{to take representative space}\\
    \email{of final document}}\\
}
\maketitle
\subfile{abstract.tex}

@@

\clearpage
\nobalance{}
\endnotetext{
  % \section{The Bleak Future of Crowd Work}
  % We've traced a path from piecework itself through
  % the processes that describe the design and implementation of piece work and crowd work as part of the same thread;
  % in tracing this process, we touched on the relationships between decomposition,
  % work \& worker abstraction,
  % flexibility, and followed through both the general fallout of crowd work in the research community
  % as well as the fallout between workers and the managers and other external parties
  % --- including researchers.

  % Throughout these case studies, we have pointed out the parallels between
  % the contemporary research in on--demand labor and
  % the much larger body of research constituting our understanding of topics such as
  % piecework, factory work, and laborer relations.
  % If we agree that this framing is useful and informative, then
  % several topics emerge as relatively open questions in the study of crowd work and on--demand labor.
  % Two of the most pressing questions are
  % \begin{inlinelist}
  % \item the beginnings of factories, and 
  % \item the decline of relevance of worker advocacy organizations.
  % \end{inlinelist}
  % We will discuss those questions here.

  % \subsection{The beginnings of factories}\label{sec:Factorization}
  % We established earlier that abstracted work and low wages tend to result in variable outcomes,
  % which presents problems for employers.
  % % So work output is variable, and that's bad. What are we doing about it?
  % Historically, this is what led to factories; by employing a cohort of known workers,
  % we can be reasonably assured that the quality of the work will be better than random.
  % Furthermore, we can invest more resources in training workers and
  % get workers to do more complex work with more context.
  % % you would pay some experts who understood what they needed to do
  % % and they would form a cohort into which you invest more.

  % This, then, suggests that the beginning of the regularization of workforces
  % --- a sort of coalescence of factories ---
  % is already happening.
  % If our framing of on--demand labor is accurately describing an underlying relationship with piecework,
  % then we should watch for the emergence and popularization of persistent teams of workers.
  % While this field site will likely prove exceedingly difficult to 
  % Social computing researchers should seek to understand this process more
  % fully, as we a

  % \subsection{The decline of advocacy organizations}

  % \section{Implications for Design}
  % If it's agreed that
  % the major topics we've discussed thus far are related and
  % --- at least to \textit{some} extent ---
  % precipitated in the fashion we argue,
  % then we have a rare opportunity as researchers,
  % and as agents of change in the communities we study,
  % to affect change on the dynamics of crowd and on--demand work
  % as they continue to develop.

  % Without claiming to have easy, cut--and--dry solutions to these problems,
  % we can nevertheless bring to attention a number of critical opportunities to
  % learn from historical parallels in piecework and factory labor,
  % and make informed decisions regarding whether
  % (or indeed how)
  % we may want to influence outcomes.
  % The challenges we bring to attention here are as follows:
  % \begin{inlinelist}
  %   \item codifying investment toward collective goods into the designs of systems;
  %   \item (re--)decentralizing the internet; and
  %   \item enabling reputation transferral.
  % \end{inlinelist}

  % \subsection{Codify the common good}
  % As \citeauthor{lessig2006code} points out in his book,
  % digital media give designers the opportunity to design and build into the systems
  % policies and practices to contribute to the collective benefit of the people therein
  % \cite{lessig2006code}.
  % Historically, the confluence of forces \citeauthor{lessig2006code} describes
  % would ultimately result in outcomes such as benefits for workers,
  % funds for sick leave and vacation, and other conveniences.
  % The transient nature of on--demand work would seem to problematize this arrangement,
  % but we can discuss and explore the viability of building into systems the mechanisms necessary
  % to save a portion of payment from every gig,
  % record taxable income, or
  % myriad other generally administrative tasks automatically.

  % \subsection{Decentralize the internet --- again}
  % Digitally mediated on--demand labor markets have historically been insular and incompatible with one another,
  % forcing workers either to choose one or juggle participation in these markets with great difficulty.
  % An ``API'' for on--demand labor markets could make it possible for any person
  % or organization to instantiate their own marketplace and inter--operate with.
  % This can be changed, and indeed must, if we are to realize the hopes of early researchers who advocated the
  % democratizing nature and power of the internet
  % \cite{barlow2009declaration,lanier2014owns}.

  % \subsection{Deal with reputation}
  % Reputation systems in on--demand labor markets are fundamentally broken.
  % To say nothing of the fact that information workers (such as those on AMT) can't transfer their reputations to qualitatively different forms of labor
  % like driving--for--hire (e.g. Uber), even within the same industry
  % it's currently not feasible for workers to transfer their reputations or other information from one place to another.
  % This affects more than the reputation and trustworthiness of workers;
  % accounting for things such as taxes, benefits, etc\dots is all but left to the individual workers, who struggle with myriad bureaucratic obstacles.
  % We can design systems that facilitate the aggregation and, more importantly, the transferral of reputation, income, and other features of work.

  % \section{Discussion}
  % We've discussed a number of aspects of on--demand work that
  % offer parallels with historical piecework.
  % Perhaps more importantly, we've hopefully demonstrated that the dynamics we observe in on--demand work
  % are interrelated and follow from one another just as necessarily as they did in
  % the development and maturation of piecework and factory work through the \nth{20} century.
  % This framing on on--demand work should, we hope, provide us with the necessary historical context
  % to make better--informed design decisions about how we want ``the future of crowd work'' to look.

  % \section{Conclusion}
  % \citeauthor{crowdworkFuture} discussed many of the challenges and problems in crowd work in \citeyear{crowdworkFuture},
  % but didn't necessarily situate the notion of crowd work in a broader context.
  % This paper attempts to fill that gap, and in doing so hopes
  % to give the research community theoretical grounding to work with and within on--demand labor more successfully.
  % But more than that, we hope to have addressed important questions to inform how we actually might make crowd work
  % a career in which we want our children to work.
}
% \theendnotes

>>>>

\usepackage{xr-hyper}
\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles,appendix,endnotes}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth,endnotes,cleveref,textcase}
\usepackage[normalem]{ulem}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{mfirstuc,lastpage}
\usepackage[en-GB]{datetime2}
\usepackage{fancyhdr}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={\plaintitle},
% Use \plainauthor for final version.
  pdfauthor={\plainauthor},
  % pdfauthor={\emptyauthor},
  pdfkeywords={\plainkeywords},
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=linkColor,
  breaklinks=true,
  hypertexnames=false
}

\bibliography{references}

@@

\renewcommand{\headrulewidth}{0pt}

% \renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\footnotesize}{\normalsize} % i don't need small text! (no but really remove this before submitting)
\begin{document}
\renewcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\renewcommand{\joke}[1]{} % don't do anything with \jokes! Just throw them away! (Better to drop it than accidentally include it)
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}

@@

\numberofauthors{3}
\author{%
  \alignauthor{Ali Alkhatib\\
    \affaddr{Stanford University}\\
    \affaddr{Stanford, USA}\\
    \email{ali.alkhatib@cs.stanford.edu}}\\
  \alignauthor{Michael Scott Bernstein\\
    \affaddr{Stanford University}\\
    \affaddr{Stanford, USA}\\
    \email{msb@cs.stanford.edu}}\\
  \alignauthor{Margaret Levi\\
    \affaddr{CASBS}\\
    \affaddr{Stanford, USA}\\
    \email{mlevi@stanford.edu}}\\
}
% \author{
% \alignauthor{Anonymized for Review\\
% \affaddr{~}\\
%     \affaddr{~}\\
%     \email{~}}\\
% }
\maketitle
\subfile{abstract.tex}

@@

\clearpage
\nobalance{}
\endnotetext{
}
